Relationship between solar wind, $D_{st}$, and plasmasphere mass density on on-hour time scales

### 2015-06-02 paper.tex
Added changes

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}

@@

\begin{document}
\title{Relationship solar wind, $D_{st}$, and plasmasphere mass density on on-hour time scales}
\author{Victoir Veibell\footnote{vveibell@gmu.edu}}
\author{R.S. Weigel\footnote{rweigel@gmu.edu}}

@@

\twocolumn[
  \begin{@twocolumnfalse}
\maketitle
\hrule
\begin{abstract}
We consider solar wind conditions surrounding time intervals of large negative excursions of the $D_{st}$ index and large positive excursions of plasmaspheric mass density. Consistent with previous results, that a sudden decrease in $D_{st}$ is associated with an increase in equatorial mass density.  We find ...
\vspace{2em}
\end{abstract}
 \end{@twocolumnfalse}
  ]

% while adding a level of depth and specification to the applicability of their results. It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.

@@

%This paper intends to investigate solar wind and magnetospheric conditions immediately before geomagnetic storm onset to determine trends and useful correlations, specifically looking at the effects on equatorial mass density ($\rho_{eq}$).

In this paper we test the relationship of short timescale effects on mass density from $D_{ST}$, $F_{10.7}$, and $B_Z$, in comparison to the long time scales presented in \cite{Takahashi2010,Takahashi2006}, as well as looking at other preconditioning factors by analysis of hourly data within a day surrounding storm onsets.

@@

%I think this opening is cliche by now. (Although I am guilty of using it.)
%Storms consisting of high energy particles in the magnetosphere have the capacity to damage satellites and ground-based electrical systems. Learning how they behave and what sort of preconditioning goes into making stronger storms helps to forecast storms and mitigate damage caused.

% does't -> does not.  Contractions are colloq.
\cite{Takahashi2006} considered the relaptionship between geomagnetic activity and average ion mass ($M$).  A scatter plot of log$_{10}(M)$ versus $-D_{st}$ showed an increasing trend.  The scatter plot of log$_{10}(M)$ versus $K_p$ had near zero correlation, but a positive trend was found when log$_{10}(M)$ versus 1.5-day averaged $K_p$ was considered, and this trend persisted when 3-day averages were used.

% I use ``state'' when I mean ``said, but I don't necessarily agree with some aspect of the analysis''.  The sentence containing the word ``state'' is usually followed by a sentence starting with ``However''.
\cite{Takahashi2010} found that spikes in the Disturbance Storm Time ($D_{ST}$) index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8$R_E$. For five storms over a 20 day period two had $\rho_{eq}$ spikes after the $D_{ST}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$. They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{ST}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{ST}$ measurements.

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{abstract}

@@

\begin{document}
\title{Relationship between solar wind, $D_{st}$, and plasmasphere mass density on on-hour time scales}
\author{
Victoir Veibell\footnote{vveibell@gmu.edu}
\and
R.S. Weigel\footnote{rweigel@gmu.edu}}

@@

\twocolumn[
  \begin{@twocolumnfalse}
\maketitle
\hrule
\begin{abstract}
We consider solar wind conditions surrounding time intervals of large negative excursions of the $D_{st}$ index and large positive excursions of plasmaspheric mass density. Consistent with previous results, a sudden decrease in $D_{st}$ is associated with an increase in equatorial mass density.  We find ...
\vspace{2em}
\end{abstract}
 \end{@twocolumnfalse}
  ]

\saythanks
% while adding a level of depth and specification to the applicability of their results. It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.

@@

%This paper intends to investigate solar wind and magnetospheric conditions immediately before geomagnetic storm onset to determine trends and useful correlations, specifically looking at the effects on equatorial mass density ($\rho_{eq}$).
In this paper we test the relationship of short timescale effects on mass density from $D_{ST}$, $F_{10.7}$, and $B_Z$, in comparison to the long time scales presented in \cite{Takahashi2010,Takahashi2006}, as well as looking at other preconditioning factors by analysis of hourly data within a day surrounding storm onsets.

@@

\cite{Takahashi2006} considered the relationship between geomagnetic activity and average ion mass ($M$).  A scatter plot of log$_{10}(M)$ versus $-D_{st}$ showed an increasing trend.  The scatter plot of log$_{10}(M)$ versus $K_p$ had near zero correlation, but a positive trend was found when log$_{10}(M)$ versus 1.5-day averaged $K_p$ was considered, and this trend persisted when 3-day averages were used.

\cite{Takahashi2010} found that spikes in the Disturbance Storm Time ($D_{ST}$) index coincide with with significant changes in $\rho_{eq}$ at an L-shell of 6.8$R_E$. For five storms over a 20 day period two had $\rho_{eq}$ spikes after the $D_{ST}$ drop, two had $\rho_{eq}$ spikes before the drop, and one showed little change in $\rho_{eq}$. They then show an epoch analysis where $\rho_{eq}$ is seen to spike the day of a $D_{ST}$ drop, using a daily average of 30 minute $\rho_{eq}$ and one hour $D_{ST}$ measurements.
